Articles of Association of London Hackspace Ltd

### 2017-11-14 constitution/articles-body.tex
Clarify that a member must be banned before being removed
Update articles for 2017 EGM changes

\item
  The association has power to do anything which is calculated to further
  its Objects or is conducive or incidental to doing so. In
  particular, the association has power:
  \begin{enumerate}
  \item
    to raise funds. 
  \item
    to buy, take on lease or in exchange, hire or otherwise acquire any
    property and to maintain and equip it for use;
  \item
    to sell, lease or otherwise dispose of all or any part of the
    property belonging to the association.  
  \item
    to borrow money and to charge the whole or any part of the property
    belonging to the association as security for repayment of the money
    borrowed or as security for a grant or the discharge of an
    obligation.
  \item
    to acquire, merge with or to enter into any partnership or joint
    venture arrangement with any other association;
  \item
    to set aside income as a reserve against future expenditure but
    only in accordance with a written policy about reserves;
  \item
    to employ and remunerate such staff as are necessary for carrying
    out the work of the association. The association may employ or remunerate a
    director only to the extent it is permitted to do so by article \ref{cls:income-property}
    and provided it complies with the conditions in that article;
  \item
    to:
    \begin{enumerate}
    \item
      deposit or invest funds; and
    \item
      employ a professional fund-manager.
    \end{enumerate}
  \item
    to provide indemnity insurance for the directors.
  \item
    to pay out of the funds of the association the costs of forming and
    registering the association;
  \end{enumerate}

@@

\item
  \label{cls:subscribers}
  \begin{enumerate}
  \item
    The subscribers to the memorandum are the first members of the association.
  \item
    Membership is open to other individuals or organisations who:
    \begin{enumerate}
    \item
      apply to the association in the form required by the directors;
    \item
      supply a valid e-mail address; and
    \item
      are approved by the directors
    \end{enumerate}
  \item

@@

\item
  Membership is terminated if:
  \begin{enumerate}
  \item
    the member dies or, if it is an organisation, ceases to exist;
  \item
    the member resigns by written notice to the association unless, after
    the resignation, there would be fewer than three members;
  \item
    any sum due from the member to the association is not paid in full
    within two weeks of it falling due;
  \item
    the member is removed from membership by a resolution of the
    directors that it is in the best interests of the association that his
    or her or its membership is terminated. Such a resolution may only be
    passed after the Board has exhausted all other options under the
    Grievance Procedure.
\end{enumerate}

@@

\item
  \begin{enumerate}
  \item
    No business shall be transacted at any general meeting unless a
    quorum is present.
  \item
    A quorum is 10 members present in person or by proxy and entitled to vote upon
      the business to be conducted at the meeting.
  \item
    The authorised representative of a member organisation shall be
    counted in the quorum.
  \end{enumerate}

@@

\item
  Any objection to the qualification of any voter must be raised at
  the meeting at which the vote is tendered and the decision of the
  person who is chairing the meeting shall be final.
\item
  \begin{enumerate}
  \item
    Any organisation that is a member of the association may nominate any
    person to act as its representative at any meeting of the association.
  \item
    The organisation must give written notice to the association of the
    name of its representative. The representative shall not be
    entitled to represent the organisation at any meeting unless the
    notice has been received by the association. The representative may
    continue to represent the organisation until written notice to the
    contrary is received by the association.
  \item
    Any notice given to the association will be conclusive evidence that
    the representative is entitled to represent the organisation or
    that his or her authority has been revoked. The association shall not
    be required to consider whether the representative has been
    properly appointed by the organisation.
  \end{enumerate}

@@

\section{Directors Elections}
\item
  \begin{enumerate}
    \item Directors elections must be called by the Board
      \begin{enumerate}
        \item in the case of the first election: before the end of the calendar year following
                the year in which the association was created.
        \item in the case of subsequent elections: before the end of the calendar year following
                the year in which the last election was held.
      \end{enumerate}
    \item
      The directors election must be carried out by electronically polling the membership as follows:
      \begin{enumerate}
        \item The Meek STV voting method must be used.
        \item All members of the association at the time the election commences are eligible to vote.
        \item The voting period of the election must be no less than 14 days and no more than 28 days.
        \item The quorum of the election must be at least 10\% of eligible voters.
      \end{enumerate}
    \item A director standing for re-election will remain a director until the successful conclusion
          of the election.
    \item A director retiring and not standing for re-election will cease to be a director at the
          start of the election.
    \item Notice of the election must be given at the time the election starts to all members eligible
          to vote who have registered an electronic mail address with the association.
   \end{enumerate}

@@

\item
  \begin{enumerate}
  \item
    The directors may from time to time make such reasonable and proper
    rules or bye laws as they may deem necessary or expedient for the
    proper conduct and management of the association.
  \item
    The bye laws may regulate the following matters but are not
    restricted to them:
    \begin{enumerate}
    \item
      the admission of members of the association (including the admission of
      organisations to membership) and the rights and privileges of such
      members, and the entrance fees, subscriptions and other fees or
      payments to be made by members;
    \item
      the conduct of members of the association in relation to one another,
      and to the association's employees and volunteers;
    \item
      the setting aside of the whole or any part or parts of the
      association's premises at any particular time or times or for any
      particular purpose or purposes;
    \item
      the procedure at general meetings and meetings of the directors in
      so far as such procedure is not regulated by the Companies Acts or
      by the articles;
    \item
      generally, all such matters as are commonly the subject matter of
      company rules.
    \end{enumerate}
  \item
    The association in general meeting has the power to alter, add to or
    repeal the rules or bye laws.
  \item
    The directors must adopt such means as they think sufficient to
    bring the rules and bye laws to the notice of members of the
    association.
  \item
    The rules or bye laws shall be binding on all members of the
    association. No rule or bye law shall be inconsistent with, or shall
    affect or repeal anything contained in, the articles.
  \end{enumerate}

>>>>

\item
  The association has power to do anything which is calculated to further
  its Objects or is conducive or incidental to doing so. In
  particular, the association has power:
  \begin{enumerate}
  \item
    to raise funds. 
  \item
    to buy, take on lease or in exchange, hire or otherwise acquire any
    property and to maintain and equip it for use;
  \item
    to sell, lease or otherwise dispose of all or any part of the
    property belonging to the association.  
  \item
    to borrow money and to charge the whole or any part of the property
    belonging to the association as security for repayment of the money
    borrowed or as security for a grant or the discharge of an
    obligation.
  \item
    to acquire, merge with or to enter into any partnership or joint
    venture arrangement with any other association;
  \item
    to set aside income as a reserve against future expenditure but
    only in accordance with a written policy about reserves;
  \item
    to employ and remunerate such staff as are necessary for carrying
    out the work of the association. The association may employ or remunerate a
    director only to the extent it is permitted to do so by
    article~\ref{cls:income-property} and provided it complies with the conditions
    in that article;
  \item
    to:
    \begin{enumerate}
    \item
      deposit or invest funds; and
    \item
      employ a professional fund-manager.
    \end{enumerate}
  \item
    to provide indemnity insurance for the directors.
  \item
    to pay out of the funds of the association the costs of forming and
    registering the association;
  \end{enumerate}

@@

\item
  \label{cls:subscribers}
  \begin{enumerate}
  \item
    The subscribers to the memorandum are the first members of the association.
  \item
    Membership is open to other individuals who:
    \begin{enumerate}
    \item
      apply to the association in the form required by the directors;
    \item
      supply a valid e-mail address; and
    \item
      are approved by the directors
    \end{enumerate}
  \item

@@

\item
  Membership is terminated if:
  \begin{enumerate}
  \item
    the member dies;
  \item
    the member resigns by written notice to the association unless, after
    the resignation, there would be fewer than three members;
  \item
    any sum due from the member to the association is not paid in full
    within two weeks of it falling due;
  \item
    the member is removed from membership by a resolution of the
    directors that it is in the best interests of the association that his
    or her or its membership is terminated. Such a resolution may only be
    passed after the Board has banned the member under the Grievance Procedure;
  \item
    A special resolution is passed stating that it is in the best interests of
    the association that his/her membership is terminated. Such a resolution may
    only be passed if the member has been given 14 days' notice of the resolution,
    and has been allowed to provide a statement to the general meeting.'
\end{enumerate}

@@

\item
  \begin{enumerate}
  \item
    No business shall be transacted at any general meeting unless a
    quorum is present.
  \item
    A quorum is 10 members present in person or by proxy and entitled to vote upon
      the business to be conducted at the meeting.
  \end{enumerate}

@@

\item
  Any objection to the qualification of any voter must be raised at
  the meeting at which the vote is tendered and the decision of the
  person who is chairing the meeting shall be final.

@@

\section{Directors Elections}
\item
  \begin{enumerate}
    \item Directors elections must be called by the Board
      \begin{enumerate}
        \item in the case of the first election: before the end of the calendar year following
                the year in which the association was created.
        \item in the case of subsequent elections: before the end of the calendar year following
                the year in which the last election was held.
      \end{enumerate}
    \item
      The directors election must be carried out by electronically polling the membership as follows:
      \begin{enumerate}
        \item The Meek STV voting method must be used.
        \item All members of the association at the time the election commences are eligible to vote.
        \item The voting period of the election must be no less than 14 days and no more than 28 days.
        \item The quorum of the election must be at least 10\% of eligible voters.
      \end{enumerate}
    \item A director standing for re-election will remain a director until the successful conclusion
          of the election.
    \item A director retiring and not standing for re-election will cease to be a director at the
          start of the election.
    \item Notice of the election must be given at the time the election starts to all members eligible
          to vote who have registered an electronic mail address with the association.
    \item The number of directors to be elected will be decided by the Board, subject to Article 23(b),
          but must not be less than two. This number should be included in the notice of election.
   \end{enumerate}

@@

\item
  \begin{enumerate}
  \item
    The directors may from time to time make such reasonable and proper
    rules or bye laws as they may deem necessary or expedient for the
    proper conduct and management of the association.
  \item
    The bye laws may regulate the following matters but are not
    restricted to them:
    \begin{enumerate}
    \item
      the admission of members of the association and the rights and
      privileges of such members, and the entrance fees, subscriptions
      and other fees or payments to be made by members;
    \item
      the conduct of members of the association in relation to one another,
      and to the association's employees and volunteers;
    \item
      the setting aside of the whole or any part or parts of the
      association's premises at any particular time or times or for any
      particular purpose or purposes;
    \item
      the procedure at general meetings and meetings of the directors in
      so far as such procedure is not regulated by the Companies Acts or
      by the articles;
    \item
      generally, all such matters as are commonly the subject matter of
      company rules.
    \end{enumerate}
  \item
    The association in general meeting has the power to alter, add to or
    repeal the rules or bye laws.
  \item
    The directors must adopt such means as they think sufficient to
    bring the rules and bye laws to the notice of members of the
    association.
  \item
    The rules or bye laws shall be binding on all members of the
    association. No rule or bye law shall be inconsistent with, or shall
    affect or repeal anything contained in, the articles.
  \end{enumerate}
